Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-04-01 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
Relecture globale et correction de coquilles

\subsection{Training and evaluation protocol}
Only CmBERT and CmBERT+ptrn are considered since the first experiment shows that SpaCy NER is outperformed for all sizes of training sets.
We leave Kraken aside as its performance hinders the projection of NER labels from the ground truth, thus dramatically reducing the size of labelled sets.
Because the NER metrics are entity-wise, they may underestimate the NER performances on stronly noised texts with fragmented entities.
We leverage the labelled sets of entries NER-\emph{reference}, NER-\emph{pero} and NER-\emph{tesseract} created as explained in \cref{sec:dataset}.
Each dataset is split into training development, and test sets following the same protocol as described in \cref{sec:ner-xp1-protocol}, except this time we do not need to create smaller training sets.
As the NER sets contain $8,341$ entries (see \cref{sec:dataset-for-eval}), the produced train sets (resp. development and test) count $6,004$ entries - 72\% of the total (resp. 668 - 8\% and $1,669$ - 20\%).
CmBERT and CmBERT+ptrn are fine-tuned on the training sets built from NER-\emph{reference} and NER-\emph{pero}.
The training parameters are mostly the same as in \cref{sec:ner-xp1-protocol}, only this time the patience threshold is set to 5 evaluations.
Finally the metrics are measured against the three tests sets.

@@

In our tests, pre-training the model brings a slight gain in performance ($\approx 0.5\%$).
We did not pre-train or fine-tune with texts extracted with Tesseract.
However, despite a loss of performance, the model pre-trained and fine-tuned on NER-pero still gives the best results.
This is probably due to the fact that the texts produced by \peroocr feature characteristics intermediary between human transcriptions and Tesseract.
This OCR tool removes the characters recognised with low confidence, which is probably a great help to the NER.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}NER F1-scores in presence of OCR noise in the training and testing sets, grouped by test set. The dataset used for training is noted in indice after the model name (e.g. CmBERT$_{pero}$ for CmBERT fine-tuned on NER-\emph{pero}).}
\end{figure}

>>>>

\subsection{Training and evaluation protocol}
Only CmBERT and CmBERT+ptrn are considered since the first experiment shows that SpaCy NER is outperformed for all sizes of training sets.
We leave Kraken aside as its performance hinders the projection of NER labels from the ground truth, thus dramatically reducing the size of labelled sets.
Because the NER metrics are entity-wise, they may underestimate the NER performances on very noisy texts with fragmented entities.
We leverage the labelled sets of entries NER-\emph{reference}, NER-\emph{pero} and NER-\emph{tesseract} created as explained in \cref{sec:dataset}.
Each dataset is split into training development, and test sets following the same protocol as described in \cref{sec:ner-xp1-protocol}, except this time we do not need to create smaller training sets.
As the NER sets contain $8,341$ entries (see \cref{sec:dataset-for-eval}), the produced train sets (resp. development and test) count $6,004$ entries - 72\% of the total (resp. 668 - 8\% and $1,669$ - 20\%).
CmBERT and CmBERT+ptrn are fine-tuned on the training sets built from NER-\emph{reference} and NER-\emph{pero}.
The training parameters are mostly the same as in \cref{sec:ner-xp1-protocol}, only this time the patience threshold is set to 5 evaluations.
Finally the metrics are measured against the three tests sets.

@@

In our tests, pre-training the model brings a slight gain in performance ($\approx 0.5\%$).
We did not pre-train or fine-tune with texts extracted with Tesseract.
However, despite a loss of performance, the model pre-trained and fine-tuned on NER-pero still gives the best results.
This is probably due to the fact that the texts produced by \peroocr feature characteristics intermediary between human transcriptions and texts produced by Tesseract.
This OCR tool removes the characters recognised with low confidence, which is probably a great help to the NER.

\begin{figure}
    \centering
    \includegraphics[width=0.90\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}NER F1-scores in presence of OCR noise in the training and testing sets, grouped by test set. The dataset used for training is noted in indice after the model name (e.g. CmBERT$_{pero}$ for CmBERT fine-tuned on NER-\emph{pero}).}
\end{figure}
